Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-09-10 paper/paper.tex
very minor tweaks to Methods wording

The wildtype and synonymously barcoded viruses were mixed with the goal of adding equal numbers of transcriptionally active HA-expressing virions of each virus strain.
The cells were then infected with this mixture at a dose designed to infect about 50\% of cells.
Infections were allowed to proceed for 12 hours.
The cells were then trypsinized, the trypsin was quenched with D10 media, and cells were resuspended in de-gassed PBS supplemented with 0.5\% bovine serum albumin and 5 mM EDTA. 
To enrich IFN+ cells, the cells were then incubated with anti-LNGFR MACSelect Microbeads (Miltenyi Biotec) and twice passed over an MS magnetic column (Miltenyi Biotec), retaining the bound (and presumably IFN-enriched) population each time. 
This MACS sorting is expected to give approximately the enrichment for IFN+ cells shown in \FIGSUPP[experiment]{MACS}.
The original, unsorted, population was then added back in to approximately 10\% of the final cell fraction in order to ensure the presence of interferon negative cells. 
At this point, uninfected MDCK-SIAT1 cells were also added to approximately 10\% of the final cell fraction to enable quantification of the cell multiplet rate (\FIG{experiment}B) and background viral mRNA in uninfected cells (\FIG{experiment}D). 
Preparation of samples for single cell analysis added an extra hour to the process, and thus the cells were analyzed at a final time point of 13 hours post infection.
The final cell suspension was counted using a disposable hemocytometer and loaded on the 10x Genomics Chromium instrument~\citep{zheng2017massively}, targeting capture of $\sim$1,500 cells.

>>>>

The wildtype and synonymously barcoded viruses were mixed with the goal of adding equal numbers of transcriptionally active HA-expressing virions of each virus strain.
The cells were then infected with this mixture at a dose designed to infect about half the cells (\FIG{experiment}D suggests that the actual rate of detectable infection was slightly lower).
Infections were allowed to proceed for 12 hours.
The cells were then trypsinized, the trypsin was quenched with D10 media, and cells were resuspended in de-gassed PBS supplemented with 0.5\% bovine serum albumin and 5 mM EDTA. 
To enrich IFN+ cells, the cells were then incubated with anti-LNGFR MACSelect Microbeads (Miltenyi Biotec) and twice passed over an MS magnetic column (Miltenyi Biotec), retaining the bound (and presumably IFN-enriched) population each time. 
This MACS sorting is expected to give approximately the enrichment for IFN+ cells shown in \FIGSUPP[experiment]{MACS}.
The original, unsorted, population was then added back in to approximately 10\% of the final cell fraction in order to ensure the presence of interferon negative cells. 
At this point, uninfected MDCK-SIAT1 cells were also added to approximately 10\% of the final cell fraction to enable quantification of the cell multiplet rate (\FIG{experiment}B) and background viral mRNA in uninfected cells (\FIG{experiment}D). 
Preparation of samples for single cell analysis (which was performed at room temperature) added an extra hour to the process after cell collection, and thus we consider the cells to have been analyzed at 13 hours post infection.
The final cell suspension was counted using a disposable hemocytometer and loaded on the 10x Genomics Chromium instrument~\citep{zheng2017massively}, targeting capture of $\sim$1,500 cells.
